---
title: "Homework 5"
author: "Xinyi Lin"
date: "11/1/2018"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)

```

# Problem One

```{r}
hw5_data_df = tibble(list.files("./data")) %>% 
  janitor::clean_names() %>% 
  mutate(files_name_wd = str_c("./data/", list_files_data),
         files_name = str_replace(list_files_data, ".csv", "")) %>% 
  select(-list_files_data)

head(hw5_data_df)
```

```{r, message = FALSE}
hw5_tidied_data =
  hw5_data_df %>% 
  mutate(data = map(files_name_wd, read_csv)) %>% 
  bind_rows() %>% 
  unnest() %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  select(-files_name_wd) %>% 
  separate(files_name, into = c("groups", "id"), sep = "_") %>% 
  mutate(week = str_replace(week, "week_", "")) %>% 
  mutate(week = as.numeric(week)) %>% 
  mutate(value = as.numeric(value)) 

head(hw5_tidied_data)
```

```{r}
hw5_tidied_data %>% 
  ggplot(aes(x = week, y = value, color = id)) +
  #geom_point() +
  geom_line() +
  facet_grid(.~ groups)
```

Through this plot, we can find that the values of subjects in two groups are similar at the beginning. However, the values of subjects in experiment group increased over time while the values of subjects in control group keep the same.

# Problem Two

## Tidied data

First, I create a `city_state` variable by combining `city` and `state`. As there is only one record about "Tulsa, AL", I think it infact happened in "Tulsa, OK" but recorded as "Tulsa, AL" mistakenly, so I changed it to "Tulsa, OK".

```{r}
homicide_df = read_csv("homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  mutate(city_state = str_replace(city_state, "Tulsa, AL", "Tulsa, OK"))
```

The original dataset gathered information about homicides in 50 large U.S. cities including the location of the killing, whether an arrest was made and, in most cases, basic demographic information about each victim. It cantains `r ncol(homicide_df)` variables and `r nrow(homicide_df)` observations. Main variables are `city`, `state` and `disposition`

## Number of total and unsolved homicides

```{r}
city_total_homicides =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarise(total_num = n()) %>% 
  arrange(desc(total_num))

head(city_total_homicides)
```

```{r}
city_unsolved_homicides =
  homicide_df %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  #summarise(n = n()) %>%
  summarise(unsolved_num = n()) %>%
  arrange(desc(unsolved_num))

head(city_unsolved_homicides)
```

## Proportion of Baltimore and MD

```{r}
two_cities_total_homicides = 
  city_total_homicides %>% 
  filter(city_state == "Baltimore, MD")

two_cities_unsolved_homicides =
  city_unsolved_homicides %>% 
  filter(city_state == "Baltimore, MD")

prop_Baltimore = 
  prop.test(two_cities_unsolved_homicides$unsolved_num, two_cities_total_homicides$total_num)

prop_Baltimore %>% 
  broom::tidy() %>% 
  pull(estimate)

prop_Baltimore %>% 
  broom::tidy() %>% 
  pull(conf.low)

prop_Baltimore %>% 
  broom::tidy() %>% 
  pull(conf.high)
```

```{r}
city_homicides = left_join(city_total_homicides, city_unsolved_homicides, by = "city_state")
  
city_homicides[is.na(city_homicides)] = 0
```

```{r}
city_prop = 
  city_homicides %>% 
  mutate(parameters = map2(city_homicides$unsolved_num, city_homicides$total_num, prop.test)) %>% 
  mutate(parameters = map(parameters, broom::tidy)) %>% 
  unnest() %>% 
  janitor::clean_names() 

head(city_prop)
```

## Draw a plot

```{r}
city_prop %>% 
  mutate(city_state = fct_reorder(city_state, desc(estimate))) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



